Ceph Parallel File System Evaluation Report

### 2013-11-07 background.tex
add ack, paper, background

Ceph\cite{Weil:2006:Ceph} is a distributed storage system designed for
scalability, reliability, and performance.  The system is based on a
distributed object storage service called RADOS (reliable autonomic distributed
object store) that manages the distribution, replication, and migration of
objects.  On top of that reliable storage abstraction Ceph builds a range of
services, including a block storage abstraction (RBD, or rados block device)
and a cache-coherent distributed file system (CephFS).

Data objects are distributed across Object Storage Devices (OSD), which refers
to either physical or logical storage unit, using CRUSH\cite{Weil:2006:Crush},
a deterministic hashing function that allows administrators to define flexible
placement policies over a hierarchical cluster structure (e.g., disks, hosts,
racks, rows, datacenters).  The location of objects can be calculated based on
the object identifier and cluster layout (similar to consistent
hashing~\cite{karger1997consistent}), thus there is no need for a metadata
index or server for the RADOS object store.
%Further, because CRUSH provides an authoritative view of data placement,
%storage daemons can coordinate directly to handle data replications,
%recovery, or object migration in the face of failure or cluster topology
%changes.  
A small cluster of monitors (ceph-mon daemons) use Paxos to provide consensus
on the current cluster layout, but do not need to explicitly coordinate
migration or recovery activities.

@@

While we are interested in Ceph for its ability to support alternative
workloads that are not easily accomplished with Lustre, in this study we are
investigating the use Ceph for future large-scale scientific HPC storage
deployments. This paper presents our experience, results, and observations in
measuring the scalability and performance of Ceph.

>>>>

Ceph\cite{Weil:2006:Ceph} is a distributed storage system designed for
scalability, reliability, and performance.  The system is based on a
distributed object storage service called RADOS (reliable autonomic distributed
object store) that manages the distribution, replication, and migration of
objects.  On top of that reliable storage abstraction Ceph builds a range of
services, including a block storage abstraction (RBD, or Rados Block Device)
and a cache-coherent distributed file system (CephFS).

Data objects are distributed across Object Storage Devices (OSD), which refers
to either physical or logical storage units, using CRUSH\cite{Weil:2006:Crush},
a deterministic hashing function that allows administrators to define flexible
placement policies over a hierarchical cluster structure (e.g., disks, hosts,
racks, rows, datacenters).  The location of objects can be calculated based on
the object identifier and cluster layout (similar to consistent
hashing~\cite{karger1997consistent}), thus there is no need for a metadata
index or server for the RADOS object store.
%Further, because CRUSH provides an authoritative view of data placement,
%storage daemons can coordinate directly to handle data replications,
%recovery, or object migration in the face of failure or cluster topology
%changes.  
A small cluster of monitors (ceph-mon daemons) use Paxos to provide consensus
on the current cluster layout, but do not need to explicitly coordinate
migration or recovery activities.

@@

While we are interested in Ceph for its ability to support alternative
workloads that are not easily accomplished with Lustre, in this study we are
investigating the use of Ceph for future large-scale scientific HPC storage
deployments.

%This paper presents our experience, results, and observations in
%measuring the scalability and performance of Ceph.
